Statically Typed String Sanitation Inside a Python

### 2014-08-11 sanitation-psp14/sanitation-psp14-short.tex
Small changes.

The premier operation for manipulating strings in $\lambdas$ is string substitution, 
which is a familiar operation to any programmer who has used regular expressions.
The replacement operation replaces all instances of a pattern in one string with
another string; for instance, $\lsubst{a|b}{a}{c} = c$.
In order to computer the type resulting from aubstitution, we also need to compute
the result of replacing on language with another inside a given language.
Finally, just for convienance, we provide a coerce operation. The introduction of
coercion requires handling of runtime errors.

@@

@@

@@

\begin{thm}{Correctness of Input Sanitation for Translated Terms.}

@@

An implementation of a similar system as a type system extension in the programming language Ace is discussed in \cite{fulton12} and \cite{fulton13}.
The implementation only supports a special case of replacement where unsafe substrings are simply stripped.
In practice, most libraries and frameworks escape command sequences instead of stripping characters; therefore, we plan to extend our implementation with
support for the replace operation as described in this paper..

>>>>

The premier operation for manipulating strings in $\lambdas$ is string substitution, 
which is a familiar operation to any programmer who has used regular expressions.
The replacement operation replaces all instances of a pattern in one string with
another string; for instance, $\lsubst{a|b}{a}{c} = c$.
In order to compute the type resulting from aubstitution, we also need to compute
the result of replacing one language with another inside a given language.
Finally, just for convienance, we provide a coerce operation. The introduction of
coercion requires handling of runtime errors.

@@

\ 
\newpage
\ 
\newpage
\

@@

The main theorem of this paper is Theorem \ref{thm:main}. Establishing this result requires an additional theorem (Theorem \ref{tcorrect}), which establishes a relationship between canonical forms for the string fragments of $\lambdas$ and $\lambdap$.

@@

\begin{thm}{Correctness of Input Sanitation for Translated Terms.}\label{thm:main}

@@

In this section, we present an example atlang program using our extension together
with our implementation of the extension in Atlang modulo ${\sf lreplace}$.
Note that in addition to Figure \ref{fig:regex}, regular expressions in atlang
also support the {\sf \^} character, which is complementation. Complementation
is definable in terms of Figure \ref{fig:regex} whenever $\Sigma$ is
fixed.

TODO-nrf insert a pargraph or two which explains what's going on...

\subsection{An Example}

Figure \ref{fig:example} demosntrates the use of string types in atlang.
The sanitize function takes an arbitrary string and returns a string without
double quotes and left and right brackets. In this example, we use HTML
escape sequences; many variants of SQL provide their own syntax
for this as well.

TODO-nrf line by line of example.

\subsection{Extension Implementation}

TODO-nrf line by line of extension implementation as ewll.

An implementation of a similar extension as the one presented here is discussed in \cite{fulton12} and \cite{fulton13}.
Our prior work only supports a special case of replacement where unsafe substrings are completely removed.
In practice, most libraries and frameworks escape command sequences instead of stripping characters; therefore, we plan to extend our implementation with
support for the replace operation as described in this paper.
